A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-29 0_reviewer_response.tex

We added an url to the open source implementation.
\commits{
ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a
}
\paper{6. Conclusion}{
\revise{}{The presented framework is open source available at \\ \url{github.com/Ultimaker/libArachne}}
}

Remove reference to the concept of `periphery' seeing as it was not really used.
\commits{
74227189eba03d13e18249f3235680691c6ebea9 % dont introduce
10bc58dc50f314e2d86f28ae6d8532fee3d20893 % don't use
a5c0d134c106876ae0edcb201eb270b66c11462f % typo near these^ commits
}
\paper{3.3 Center classification}{
\revise{The remainder is called peripheral.}{}
}
\paper{3.5 Beading}{
Now that we have determined the bead counts in the \revise{}{marked }central regions we will describe how the \revise{peripheral}{unmarked} regions are handled.
}

Explain why and how statistics are gathered over the whole data set.
\commits{17135b010f5ac51fda77357136a19f67a80dbc33}
\paper{5.2 Computational results}
{
\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
}

Furthermore:
\begin{itemize*}
\item Removed paragraph before bullet list of contributions, because it contained the same information as the bullet list.
\commit{}
\item Removed wrapfigure explaining the area covered by a single extrusion move (in section~5.2.1~Accuracy), since that is already explained in the appendix.
\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
\item Fig.~10 and Fig.~18 colors are adjusted.
\commits{
1196bad1c2bf4fb41e7d28985938cfe678384e5a % fig 10
43cadb352a6a276bbaaab53f9b5b217bec4b3a2e
}
\item Fixed double header of References.
\commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}
\item Fixed various issues in References.
\commits{c524eae1a78dd1ca54293522139c44a68a911e80}
\item Fixed some typos.
\commits{5f5c4c640d94010816e6d6d5934a2dc016b4d172
1662d3c4c3aa977bddd730ac59f1bc874b9eb574 % -''See ``
b108d7de4f1e1e9676d45cf24eea263af6b8b9c7 % width => widths
9d9f02edc43689c0970a74118e44a196cc11c729 % typos
87bed1e663ea831d8f52b0ccf4ef5eebaab32ade % typo
2e21687731d95a9a1315206531f0474fb924c6eb % spell check
}
\item Our department has changed its name to \emph{Sustainable} Design Engineering.
\commits{
442a5df5a4f27f1ce94a5ef298a1f7bcc3df934d
}
\end{itemize*}

### 2020-01-29 1_intro.tex
remove contributions paragraph in favor of bullet list

In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
\revise{
For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
}{Furthermore we present an approach to accurately realize adaptive bead width.
}
See \cref{intro_wedge_distributed}. 
% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
% Some such toolpath generation techniques have already been developed.

>>>>

\revise{
In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
See \cref{intro_wedge_distributed}. 
}{}
